Tungsten Disulfides and Tungsten Oxides Core-Shell NWs

### 2014-03-09 BackMatter/paper.tex
a low productivity week

@@

@@

@@

equation embodies the law of conservation

become varied, laptop not hammer it hand, bubble pop, crash and burns. exert a marked influence

>>>>

Electronic structure of \ce{MoS2}.\cite{Eknapakul2014} K intercalating into bulk to create quasi-standing 1L. Large effective mass 0.6 $m_e$ found, implying low mobility. Direct gap 1.88eV is measured.

@@

a single nanowire tends to minimize its surface. 2D isoperimetric quotient or circularity $C= \frac{4\pi A}{P^2}$, where A is area and P is perimeter of the cross-section.

@@

photocatalyst review.\cite{Mills1997} Definition: catalysis should not be used unless it can be demonstrated that the turnover number\footnote{the number of product molecules per number of active sites.} is greater than unity. Otherwise, semiconductor-assisted photoreaction is more appropriate. aerated, flush with air; nitrogen-purged. Deggussa P25 \ce{TiO2} high temperature flame hydrolysis of \ce{TiCl4} in presence of hydrogen and oxygen. Oxidization of organic species is presumably obtained by \ce{Ti^{IV}OH^{.-}}, rather than direct hole transfer. carrier decay pathways. deactivation of catalyst by intermediate product.

MB natural decoloration under sunlight is found to be about 18\%.\cite{Nogueira1993} Latitude: 24 south, $3.4mW/cm^2$. natural evaporation should be prevented or corrected.

\section{dissertation}

WS2 surface hydrophilic or hydrophobic.
\[
\cee{Ti(IV)-OCH3 + h^+ -> Ti(IV)-O^+CH3}
\]

\ce{WO3} photoanode should be a n-type semiconductor, stable in acidic aqueous solution.

Swagelok TM. List of equipments,

@@

equation embodies the law of conservation, excess, set in consequentially.

become varied, laptop not hammer it hand, bubble pop, crash and burns. exert a marked influence, detrimental impact.

theoretical interest, phase transition, water droplets, water vapor cools, supersaturates and nucleates. aerosol, sulfuric acid, subsaturated, corrosion. union, cross, T. moisture,

### 2014-03-09 ch-tms/Seeded_growth_draft.tex
a low productivity week

>>>>

 Transition metal anchored to \ce{TiO2} review.\cite{Ardo2009} molecular approach, chemical bonds afford large energy storage capacities. 
\begin{enumerate}
   \item photo excitation of dye sensitizer to form a molecular excited state;
   \item electron injection from HOMO to CB of semiconductor to cause e-h separation;
   \item oxidized(loss of electron) sensitized is compensated by external donor;
   \item external donor is compensated by the CB electron after performing useful works;
   \item this is a typical operation of Gratzel cell. 
\end{enumerate}

Metal-to-ligand charge transfer (MLCT) ($d \rightarrow \pi^*$)
